References

### 2017-04-11 cv/CoverLetter/CitiMQA_QuantitativeAnalyst.tex
1. Changed my cover letter template. 2. updated the title of the paper with Jeff.

I am currently a PhD student at Copenhagen University, researching in
Mathematical statistics and particularly in time series analysis,
extreme value theory and random matrix theory. I am available for
immediate full-time work and expect to receive my degree on 30th
September, 2017. So far I have co-authored and published two papers on
eigen systems of sample covariance matrices, with a focus on
heavy-tailed (e.g. power-law tail) time series. These results are
applicable to principle component analysis, for example.

@@

The fourth paper of mine is about estimation of the probability of very
large losses posed by portfolios whose volatility dynamics are
time series modeled by univariate GARCH(p,q) or multivariate
GARCH processes. Because the stationary distribution of such a process
is not known exactly, the aforementioned probability as well as the
related risk measures {\em Value at Risk} and {\em Expected
  Shortfall} cannot be computed precisely. In the paper I propose 
an estimator based on importance sampling and Markov chain theory and
naturally, would be more than happy to see it applied in practical
risk management. I have implemented the estimator in C++, and in
particular, have used the OpenMP directives to achieve high
performance via parallel computing.

>>>>

I am currently a PhD student at Copenhagen University, researching in
Mathematical statistics and particularly in time series analysis,
extreme value theory and random matrix theory. I will be available for
full-time work on 1st July 2017. I expect to receive my degree on 30th
September, 2017. So far I have co-authored and published two papers on
eigen systems of sample covariance matrices, with a focus on
heavy-tailed (e.g. power-law tail) time series. These results are
applicable to principle component analysis, for example.

@@

The fourth paper of mine is about estimation of the probability of very
large losses posed by portfolios whose volatility dynamics are
time series modelled by univariate GARCH(p,q) or multivariate
GARCH processes. Because the stationary distribution of such a process
is not known exactly, the aforementioned probability as well as the
related risk measures {\em Value at Risk} and {\em Expected
  Shortfall} cannot be computed precisely. In the paper I propose 
an estimator based on importance sampling and Markov chain theory and
naturally, would be more than happy to see it applied in practical
risk management. I have implemented the estimator in C++, and in
particular, have used the OpenMP directives to achieve high
performance via parallel computing.
